---
title: Fama as Measured by Google Scholar | rCharts + dygraphs
framework: bootplus
layout: poststripped
mode: selfcontained
highlighter: prettify
hitheme    : twitter-bootstrap
navbar:
  title: Eugene Fama, dygraphs, rCharts, scholar
lead : >
  October 25, 2013
assets:
  css:
  - "http://fonts.googleapis.com/css?family=Raleway:300"
  - "http://fonts.googleapis.com/css?family=Oxygen"
  jshead:
  - "./lodash.js"
  - "./dygraph-combined.js"
--- 
### Random Collection ... Love d3 but ...

If this seems like a random collection of experiments, it is.

I love my d3 and svg, but sometimes with "big" data it gets a little sluggish.  An older battle-tested canvas-based HTML5 library [`dygraphs`](http://dygraphs.com) claims

<blockquote>
Handles huge data sets: dygraphs plots millions of points without getting bogged down.
</blockquote>

Before we can test the claim I thought I would try first to plug [`dygraphs`](http://dygraphs.com) into [`rCharts`](http://rcharts.io) much like the rCharts author Ramnath Vaidyanathan explains [here](http://rcharts.io/howitworks) and in [part 2](http://rcharts.io/howitworks/part2).  Also, why not try out the new R package [`scholar`](http://www.jameskeirstead.ca/blog/new-r-package-scholar/) while we are at it to pay homage to Eugene Fama and his new Nobel Prize.

---
### R package scholar
James Keirstead's new R package [`scholar`](http://www.jameskeirstead.ca/blog/new-r-package-scholar/) offers Google scholar data in a very easy format.  As you can see below the code is very simple.  One little nuisance I found though is that not all researchers (like Ken French) have Google ids, and even if they do, we have to find them [manually](http://scholar.google.com/citations?user=yP7euFUAAAAJ&hl=en).

```{r echo=F, warning=F, error=F, message=F, cache = F}
require(knitr)
opts_chunk$set(
  echo=T,
  warning=F,
  error=F, 
  message=F,
  cache = F,
  results = 'asis',
  fig.width = 11,
  fig.height = 4
)
```

```{r}
# Fama from Google Scholar
# http://scholar.google.com/citations?user=yP7euFUAAAAJ&hl=en
# yP7euFUAAAAJ

# French from Google Scholar
# does not exist

library(scholar)
famaId = "yP7euFUAAAAJ"
fama.df <- compare_scholar_careers(famaId)
plot(fama.df$cites~fama.df$year, type = "p")
abline(lm(fama.df$cites~fama.df$year), col="green")
title(main = "Eugene Fama | Cites By Year", adj = 0.05, outer=TRUE, line = -2)
```
---
### Plot with rCharts Using dygraphs
Everything is better when it is interactive.  Let's expose `dygraphs` to `rCharts` for now as a custom implementation.

<div class = 'row'>
  <div id = "dygraphCite" class = 'span8' style = 'height:300px;'>
  </div>
</div>
<br>

```{r}
library(rCharts)

fama.df$date <- paste0(
  "#! new Date(",
  as.numeric(as.POSIXct(paste0(fama.df$year,"-12-31"))) * 1000,
  ")!#"
)

dy1 <- rCharts$new()
dy1$setLib( "." )
dy1$templates$script = "chart.html"
dy1$set(
  data = fama.df,
  x = "date",
  y = "cites",
  chart = list(
    title = "Eugene Fama - Career in Citations from Google Scholar",
    ylabel = "Citations",
    showRangeSelector = TRUE,
    labelsDivStyles= list(
      background = 'none'
    ),
    strokeWidth = 1.5
  )
)
cat(noquote(dy1$html( chartId = "dygraphCite" )))
```

So far I am very impressed with `dygraphs` and look forward to more thoroughly testing it especially with larger data sets.  Take a look at the [gallery](http://dygraphs.com/gallery/) to see its full power, mostly out of the box and accessible even with this basic rCharts implementation.  Also, there is a very lively [Google group of dygraphs-users](https://groups.google.com/forum/#!forum/dygraphs-users).

---
### Thanks
- [Ramnath Vaidyanathan](http://twitter.com/ramnath_vaidya)
- [James Keirstead](http://www.jameskeirstead.ca/)
- Dan, Alistair, Robert, and Klaus - dygraphs contributors
- [Marcello Palmitessa](http://aozora.github.io/bootplus/)